### 2013-09-09 thesis/src/chapters/chapter-4.tex
Add clients' view on cloud computing section

\subsection{Deployment models}
The informal introduction to the concept of a \emph{hybrid cloud} in the previous section requires a strict definion, but it is virtually impossible without introduction of other deployment models:
\begin{itemize}
  \item Private Cloud -- The provisioned cloud infrastructure is used exclusively by a single organization (that may consist of many business units) and may be owned, managed and operated by the organization or a third party.
  \item Public Cloud -- The provisioned cloud infrastructre is used by general public and may be owned, managed and operated by a business, academic or government organization or some combination of them. It exists on the premises of the cloud provider.
  \item Community Cloud -- The cloud infrastructure is provisioned for exclusive use by a specific community of consumers from organizations that have shared concerns (e.g., mission, security requirements, policy , and compliance considerations). It may be owned, managed , and operated by one or more of the organizations in the community, a third party, or some combination of them, and it may exist on or off premises. 
\end{itemize}
Having defined those models, we can see that \emph{hybrid cloud} can be placed among them and be defined as a model in which the provisioned infrastructure is a composition of two or more other infrastructures - \emph{private},\emph{community} or \emph{public}.

\subsection{Current usage and trends}

>>>>

\subsection{Deployment models}
The informal introduction to the concept of a \emph{hybrid cloud} in the previous section requires a strict definition, but it is virtually impossible without defining other deployment models:
\begin{itemize}
  \item Private Cloud -- The provisioned cloud infrastructure is used exclusively by a single organization (that may consist of many business units) and may be owned, managed and operated by the organization or a third party.
  \item Public Cloud -- The provisioned cloud infrastructure is used by general public and may be owned, managed and operated by a business, academic or government organization or some combination of them. It exists on the premises of the cloud provider.
  \item Community Cloud -- The cloud infrastructure is provisioned for exclusive use by a specific community of consumers from organizations that have shared concerns (e.g., mission, security requirements, policy , and compliance considerations). It may be owned, managed , and operated by one or more of the organizations in the community, a third party, or some combination of them, and it may exist on or off premises. 
\end{itemize}
Having defined those models, we can see that \emph{hybrid cloud} can be placed among them and be defined as a model in which the provisioned infrastructure is a composition of two or more other infrastructures - \emph{private},\emph{community} or \emph{public}.

\subsection{Current usage and trends}
\subsubsection*{Cloud -- clients' view}
Before digging into the details of current usage and popularity of the hybrid model, it is worth discussing the general attitude of clients towards cloud computing. As the recent survey \cite{RackspaceSurvey13} shows, the major factor that prevents companies from adopting cloud solutions is their concern over security -- in 2012 as much as 52\% responders considered it as a main concern with the regard to cloud in general. However, the tendency is that more and more enterprises do not find it a major issue as in 2012 the number declined to 46\%.
Complexity related to the managament of cloud components, Vendor lock-in, interoperability and reliability were among the most frequent obsctacles to adoption in 2013 for they constitued 46\%, 35\%, 27\% and 22.3\% of responders' votes respectively. Total results are shown in the figure \ref{ch4:cloud-computing-adoption-obstacles-2013}.
\begin{figure}[!ht]
  \begin{center}
    \includegraphics{chapter-4/cloud-computing-adoption-obstacles-2013}
  \end{center}
  \caption{Major obstacles to cloud adoption in 2013 according to \cite{RackspaceSurvey13}}
  \label{ch4:cloud-computing-adoption-obstacles-2013}
\end{figure}

\subsubsection*{View on hybrid cloud}
